### 2020-10-15 priority-gv.tex
Update priority-gv.tex

\emph{Actions} are terms which perform communication actions which synchronisation between two threads:
\begin{definition}[Actions]
  \label{def:pgv-actions}
  A~term \emph{acts on} an endpoint $\tm{x}$ if it is of the form $\tm{\send\;\pair{V}{x}}$, $\tm{\recv\;{x}}$, $\tm{\close\;{x}}$, or $\tm{\wait\;{x}}$. A~term is an \emph{action} if it acts on some endpoint $\tm{x}$.
\end{definition}

\emph{Ready terms} are terms which are ready to perform a communication action, either by themselves, \eg creating a new channel or thread, or with another thread, \eg sending or receiving:
\begin{definition}[Ready Terms]
  \label{def:pgv-ready-actions}
  A~term $\tm{L}$ is \emph{ready} if it is of the form $\tm{\plug{E}{M}}$, where $\tm{M}$ is of the form $\tm{\new}$, $\tm{\spawn\;N}$, $\tm{\link\;\pair{x}{y}}$ or $\tm{\link\;\pair{y}{x}}$, or $\tm{M}$ acts on $\tm{x}$. In the latter case, we say that $\tm{L}$ is \emph{ready to act on} $\tm{x}$.
\end{definition}

>>>>

\emph{Actions} are terms which perform communication actions and which synchronise between two threads.
\begin{definition}[Actions]
  \label{def:pgv-actions}
  A~term \emph{acts on} an endpoint $\tm{x}$ if it is of the form $\tm{\send\;\pair{V}{x}}$, $\tm{\recv\;{x}}$, $\tm{\close\;{x}}$, or $\tm{\wait\;{x}}$. A~term is an \emph{action} if it acts on some endpoint $\tm{x}$.
\end{definition}

\emph{Ready terms} are terms which are ready to perform a communication action, either by themselves, \eg creating a new channel or thread, or with another thread, \eg sending or receiving.
\begin{definition}[Ready Terms]
  \label{def:pgv-ready-actions}
  A~term $\tm{L}$ is \emph{ready} if it is of the form $\tm{\plug{E}{M}}$, where $\tm{M}$ is of the form $\tm{\new}$, $\tm{\spawn\;N}$, $\tm{\link\;\pair{x}{y}}$ or $\tm{\link\;\pair{y}{x}}$, or $\tm{M}$ acts on $\tm{x}$. In the latter case, we say that $\tm{L}$ is \emph{ready to act on} $\tm{x}$.
\end{definition}
